Thesis Title

### 2022-03-20 chapters/paper1.tex
push references

Nine body fluid samples and one tissue sample from 9 different patients were sequenced, including one sample from peritoneal fluid, five from pus (3 abscesses and 2 empyemas), two from synovial fluid of knees with prosthesis, one from sputum and one from a bone biopsy (Table \ref{tab:ch2_table_1}).
In total 15 different isolates obtained from the 10 samples were considered of possible clinical significance and were selected for species identification and antimicrobial susceptibility testing during routine work up of the samples (Table \ref{tab:ch2_table2},\ref{} and \ref{}).
In samples 2 and 3, only one colony-forming unit (CFU) of \textit{Escherichia coli} and \textit{Staphylococcus epidermidis}, respectively, was detected after 48 hours of incubation. 
In samples 2 and 5, the anaerobic cultures were mixed to such an extent, that no further characterization of the colonies was performed, and the results were reported as anaerobic mixed culture.

@@

There was fungal growth in 2 samples (1 and 5) that included two Candida species (one \textit{Candida glabrata} and one \textit{Candida albicans}). 
The different bacterial and fungal species identified in each sample are shown in Tables \ref{tab:ch2_table2}, \ref{} and \ref{}.

>>>>

Nine body fluid samples and one tissue sample from 9 different patients were sequenced, including one sample from peritoneal fluid, five from pus (3 abscesses and 2 empyemas), two from synovial fluid of knees with prosthesis, one from sputum and one from a bone biopsy (Table \ref{tab:ch2_table_1}).
In total 15 different isolates obtained from the 10 samples were considered of possible clinical significance and were selected for species identification and antimicrobial susceptibility testing during routine work up of the samples (Table \ref{tab:ch2_table2},\ref{ch2_table3} and \ref{}).
In samples 2 and 3, only one colony-forming unit (CFU) of \textit{Escherichia coli} and \textit{Staphylococcus epidermidis}, respectively, was detected after 48 hours of incubation. 
In samples 2 and 5, the anaerobic cultures were mixed to such an extent, that no further characterization of the colonies was performed, and the results were reported as anaerobic mixed culture.

@@

There was fungal growth in 2 samples (1 and 5) that included two Candida species (one \textit{Candida glabrata} and one \textit{Candida albicans}). 
The different bacterial and fungal species identified in each sample are shown in Tables \ref{tab:ch2_table2}, \ref{ch2_table3} and \ref{}.
